% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\author{}
\date{}

\begin{document}

\textbf{Lab 3 -- Quantitative Metrics}

\textbf{Data Preprocessing and Initial Challenges}

I successfully addressed two key data preprocessing challenges in my
analysis. Firstly, I resolved the issue of missing values and tackled
data type inconsistencies. Following this, I preserved the current state
of the dataset by saving it. Subsequently, I reloaded the data and
performed data standardization using the
\textquotesingle LabelEncoder\textquotesingle{} from the Scikit-Learn
library.

My analysis extended to feature selection, where I employed various
techniques to identify the most relevant columns. After rigorous
evaluation, I identified a set of 30 features that exhibited the
strongest associations with the target variable. As a result, I pruned
the remaining columns, focusing on these 30 selected features for
subsequent analysis.

\textbf{Application of Linear Regression Model}

I then applied a Linear Regression algorithm to the refined dataset and
assessed its performance. Initially, when evaluating the model on the
training data, I observed a remarkable accuracy score of 1. However,
this seemingly perfect accuracy raised concerns of overfitting,
prompting me to verify the model\textquotesingle s performance on unseen
data.

\textbf{Testing Data Evaluation and Visualization}

To evaluate the model\textquotesingle s generalization capability, I
employed a scatter plot to visualize the disparities between actual and
predicted outputs. To my satisfaction, the plot revealed a close
alignment between the two, suggesting that the model\textquotesingle s
predictions were highly accurate on the testing data.

\textbf{Quantitative Model Assessment}

To quantitatively gauge the model\textquotesingle s performance, I
calculated three common metrics: Mean Squared Error (MSE), Mean Absolute
Error (MAE), and Root Mean Squared Error (RMSE). All three metrics
consistently indicated that the model\textquotesingle s error was nearly
zero, reinforcing the conclusion that the model was performing
exceptionally well.

\textbf{High Accuracy Justification}

This exceptional accuracy can be attributed to the high correlation
observed between various features and the target variable, with some
correlations surpassing the 0.85 threshold. Moreover, the meticulous and
iterative feature selection process, which distilled the initial 55
columns down to the optimal 30, further contributed to the
model\textquotesingle s outstanding performance.

\end{document}
